Arc Blanc: a real time ocean simulation framework

### 2025-02-06 paper.tex
Update the graph with log scale

\begin{figure}[ht]
	\centering
	\subfloat{\includegraphics[width=0.5\textwidth]{Figures/interpolationAccuracyComparison.png}\label{subfig:interpolationAccuracyComparison}}
	\hfill
	\subfloat{\includegraphics[width=0.5\textwidth]{Figures/interpolationAccuracyComparisonZoom.png}\label{subfig:interpolationAccuracyComparisonZoom}}
	\caption{The left figure represents the accuracy of different type of interpolation in function of the size of the discretization $N$. The right one does a zoom on small velocities between $0$ and $0.1$.
		They use 10000 positions from a continuous uniform distribution in the parallelepiped $[-1000,1000]\times[-125,4.5]\times[-1000, 1000]$ and with a wind speed of 20 $m.s^{-1}$.
		The interpolated velocity $\tilde{\mathbf{v}}$ and the analytical velocity $\mathbf{v}$ are evaluated.
		The accuracy is defined by the mean of all positions of $\big|||\tilde{\mathbf{v}}||-||\mathbf{v}||\big|$.
		It can be noticed that considering a uniform discretization, then exponential interpolation has a better accuracy than linear one.
		Logarithmic discretization is much better than uniform discretization, whatever the used interpolation.
		At least, exponential interpolation gives slightly better result than linear interpolation, even for low $N$.}
	\label{fig:interpolationAccuracyComparison}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/interpolationAccuracyComparisonLogScale.png}\label{subfig:interpolationAccuracyComparisonLogScale}
	\caption{This figure represents the accuracy of different type of interpolation in function of the size of the discretization $N$. The accuracy axis used a logarithmic scale to be more readable.
		It uses 10000 positions from a continuous uniform distribution in the parallelepiped $[-1000,1000]\times[-125,4.5]\times[-1000, 1000]$ and with a wind speed of 20 $m.s^{-1}$.
		The interpolated velocity $\tilde{\mathbf{v}}$ and the analytical velocity $\mathbf{v}$ are evaluated.
		The accuracy is defined by the mean of all positions of $\big|||\tilde{\mathbf{v}}||-||\mathbf{v}||\big|$.
		It can be noticed that considering a uniform discretization, then exponential interpolation has a better accuracy than linear one.
		Logarithmic discretization is much better than uniform discretization, whatever the used interpolation.
		At least, for low $N$, exponential interpolation gives slightly better result than linear interpolation.}
	\label{fig:interpolationAccuracyComparison}
\end{figure}
